Astr 513: Final Project

### 2016-04-29 Final_Project/ms.tex
Tentatively done with the planck section. Can definitely go into detail on why we chose this.

\usepackage{todonotes}
\newcommand\TM[1]{\todo[color=green!40, inline, size=\small]{TM: #1}}
\newcommand\EW[1]{\todo[color=blue!40, inline, size=\small]{TM: #1}}
\newcommand\LC[1]{\todo[color=magenta!40, inline, size=\small]{TM: #1}}
\newcommand\Planck{{\it Planck}\ }

@@

\section{Planck 2015 Results}
\label{sec:planck}
In 2009 the European Space Agency launched the \Planck satellite in order
to measure the Cosmis Microwave Background (CMB) with unparalleled precision.
By measuring the small anisotropies in the temperature of the CMB across
the entire sky one calculates the angular power spectrum, which can be
predicted from first principles (see, e.g., \citet{dodelson2003}).

>>>>

\usepackage{todonotes}
\newcommand\TM[1]{\todo[color=green!40, inline, size=\small]{TM: #1}}
\newcommand\EW[1]{\todo[color=blue!40, inline, size=\small]{TM: #1}}
\newcommand\LC[1]{\todo[color=magenta!40, inline, size=\small]{TM: #1}}

\newcommand\Planck{{\it Planck}\ }
\newcommand\Cosmosis{{\it Cosmosis}\ }

@@

\section{Planck 2015 Results}
\label{sec:planck}
In 2009 the European Space Agency launched the \Planck satellite in order
to measure the Cosmis Microwave Background (CMB) with unparalleled precision.
By measuring the small anisotropies in the temperature of the CMB across
the entire sky one calculates the angular power spectrum, which can be
modeled using first principles (see, e.g., \citet{dodelson2003}).
By using a likelihood method similar to our own, the authors of
\citet{planck2013} estimated 14 nuisance parameters and 
six cosmological parameters, including the geometrical parameters,
$\Omega_M$, $\Omega_\Lambda$ and $\Omega_k$, that we use in our
SNIa analysis. The only prior used by \citet{planck2013}
on cosmological parameters was from the WMAP result \citep{wmap2011}
for the optical depth $\tau$. We do not use this parameter
in our SNIa model.

\citet{planck2013} report marginalized
posterior distributions for all parameters,
which we report in Table~XXX. This prior is implemented
in the planck2015 module implemented in \Cosmosis \citep{cosmosis}.
